---
pagetitle: Tough
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
```

### "When Things Get Tough They Just Look After Themselves"---Passenger Reactions During the COVID-19 Crisis
*Last updated:* `r format(Sys.time(), '%d %B %Y')`

```{r load data, include=FALSE}
df <- read.csv("airline_reviews.csv")
```

*Info:* All values printed in bold will be updated automatically when the data changes.

During the past week, I started to collect airline reviews in order to analyze how passenger reactions changed during the COVID-19 crisis. So far, it contains **`r nrow(filter(df, review_language == 'en'))`** English and **`r nrow(filter(df, review_language == 'de'))`** German reviews for **`r unique(df[['airline_name']])`**. For those airlines it covers all reviews posted between **`r tail(df[['review_date']], 1)`** and **`r head(df[['review_date']], 1)`**.

The data set contains the following variables. You find it [here](https://github.com/florianpethig/tough/blob/master/airline_reviews.csv).

```{r describe data, echo=FALSE}
# create dataframe
Variable <- names(df)
Description <- c('Unique review URL', 'User name', 'Unique user URL', 'Geolocation of the user', 
                 'Airline name', 'Overall rating', 'Date review was published', 'Date traveled', 'Flight length', 'Booking class', 'Origin and destination', 'City of origin', 'City of destination', 'Review title', 'Review text', 'Language')
Values <- c('','' ,'' ,'' ,toString(unique(df[['airline_name']])) ,
            '1 = terrible, 2 = poor, 3 = average, 4 = very good, 5 = excellent', '', '', 'Intercontinental, domestic, etc.', 'Economy, Premium Economy, Business, First', '', '', '', '', '', '')
df <- data.frame(Variable, Description, Values)
# show table
library(knitr)
kable(df)
```
